An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-15 draft.tex
Paper Organization

% The rest of the paper is organized as follows...

@@

\section{Multi-population design} % Is this part of the state of the
                                % art? - JJ
% Also, multipopulation design of what?x
Multi-population based methods divide the original population into
smaller subpopulations or islands, with every subpopulation carrying out the
algorithm independently, with synchronous or asynchronous communication with the
rest of the islands. % exemplify how this is done in different
                     % metaheuristics, especially those we will be
                     % using here - JJ
This relative isolation helps in maintaining an overall
diversity since each subpopulation will search in a particular area, at least
between communications. The recombination mentioned above (mixing) or migration
between subpopulations is needed to avoid a premature convergence of candidate
solutions since smaller populations are known to perform better for a given
problem than bigger populations. % Smaller populations converge
                                % prematurely or perform better? - JJ
However, it gives them the added advantage of
parallel operation. Additionally, and in some cases, multi-population algorithms
scale better than expected due to the interaction between the algorithm and the
parallelism of the operation \cite{ALBA20027}. % Need to clarify this
                                % and if it extends to Swarm
                                % algorithms too
                                % Also, is your objective to achieve this superlinear speedup? - JJ

@@

>>>>

The organization of the paper is as follows. First, in Section \ref{multi}, we present a
background of the fundamental issues of integrating nature-inspired optimization
and multi-population methods. Section \ref{soa} presents state of the art relevant to
our work. In Section \ref{method}, we present the proposed method.  Section \ref{setup} describes
the design of the empirical evaluation we designed to assess the effectiveness
of the method, and in Section \ref{results}, we report and discuss the results. Finally, we
offer the conclusions of this paper and suggestions on future work in Section \ref{conclusions}.

@@

\section{Multi-population methods} % Is this part of the state of the
\label{multi}
                                % art? - JJ
% This the Background for the design decisions, but I think is also needed
% to better understand the state of the art.

% Also, multipopulation design of what?x
Multi-population based methods divide the original population into
smaller subpopulations or islands, with every subpopulation carrying out the
algorithm independently, with synchronous or asynchronous communication with the
rest of the islands. % exemplify how this is done in different
                     % metaheuristics, especially those we will be
                     % using here - JJ
This relative isolation helps in maintaining an overall
diversity since each subpopulation will search in a particular area, at least
between communications. The recombination mentioned above (mixing) or migration
between subpopulations is needed to avoid a premature convergence of candidate
solutions since smaller populations are known to perform better for a given
problem than bigger populations. % Smaller populations converge
                                % prematurely or perform better? - JJ
However, it gives them the added advantage of
parallel operation. Additionally, and in some cases, multi-population algorithms
scale better than expected due to the interaction between the algorithm and the
parallelism of the operation \cite{ALBA20027}. % Need to clarify this
                                % and if it extends to Swarm
                                % algorithms too
                                % Also, is your objective to achieve this superlinear speedup? - JJ

@@

\section{State of the Art} 
\label{soa}

\section{Proposed Method} 
\label{method}

\section{Experimental Setup} 
\label{setup}

\section{Experimental Results} 
\label{results}

\section{Conclusions} 
\label{conclusions}
